\large \textbf{Leveraging Historical Ties between Cognitive Science and Computer Science to Guide Programming Education}

### 2016-02-04 paper.tex
Updates from ShareLaTeX

\documentclass[12pt]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[babel]{csquotes}
\usepackage{graphicx}
\usepackage{etoolbox}
\usepackage{changepage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage[margin=1in]{geometry}

%\usepackage{xunicode}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows,shapes,fit}
\usepackage{standalone}

@@

% conflict between teaching programming syntax, teaching ``how to program'', teaching high-level concepts like abstractions and how to ``do'' problem solving.
\section{Coding for everyone}
In the past few years, there has been increasing interest to get more
people, regardless of background, to learn to program. In fact,
President Obama recently made a statement calling on all children to
have the opportunity to learn about computer
science\autocite{whitehouse_computer_2016}. Sites such as code.org
promote CS education opportunities for all, citing statistics about
STEM jobs and arguing that in the 21st century knowledge about
computer science is foundational\autocite{code.org_every_2016}. Many
institutions of higher education either have programming requirements
for non-computer-science majors, or have been expanding programming to
non-majors\autocite{rich_cs1_2004,forte_motivation_2005,guzdial_design_2005}. At
the authors of this paper's institution, all first year general
engineering students are required to complete an introductory
programming module as part of their first-year engineering course, and
in general ``basic programming skills'' is a common desired outcome
across engineering
curricula\autocite{reid_classification_2014}.

@@

\section{Methods}
Assuming that there would be more comprehensive research of
introductory programming in the computer science community we began
with targeted searchs of the ACM digital library for `introductory
programming'. Once we found key papers that seemed to indicate a call
to action
\autocite[e.g.][]{mccracken_multinational_2001,kolling_problem_1999},
or a survey of practices
\autocite[e.g.][]{pears_survey_2007-1,robins_learning_2003} we used
the `cited by' list to find additional relevant papers.

>>>>

\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[babel]{csquotes}
\usepackage{graphicx}
\usepackage{etoolbox}
\usepackage{changepage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage[margin=1in]{geometry}
\usepackage{times}
%\usepackage{xunicode}
\usepackage[dvipsnames,table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows,shapes,fit}
\usepackage{standalone}
\usepackage{textcomp}

@@

% conflict between teaching programming syntax, teaching ``how to program'', teaching high-level concepts like abstractions and how to ``do'' problem solving.
\section*{Coding for everyone}
In the past few years, there has been increasing interest to get more
people, regardless of background, to learn to program. In fact,
President Obama recently made a statement calling on all children to
have the opportunity to learn about computer
science\autocite{whitehouse_computer_2016}. Sites such as code.org
promote CS education opportunities for all, citing statistics about
STEM jobs and arguing that in the 21st century knowledge about
computer science is foundational\autocite{code.org_every_2016}. Many
institutions of higher education either have programming requirements
for non-computer-science majors, or have been expanding programming to
non-majors\autocite{rich_cs1_2004,forte_motivation_2005,guzdial_design_2005}. At
the authors of this paper's institution, all first year general
engineering students are required to complete an introductory
programming module as part of their first-year engineering course, and
in general ``basic programming skills'' is a common desired outcome
across engineering
curricula\autocite{reid_classification_2014}.

@@

\section*{Methods}
Assuming that there would be more comprehensive research of
introductory programming in the computer science community we began
with targeted searchs of the ACM digital library for `introductory
programming'. Once we found key papers that seemed to indicate a call
to action
\autocite[e.g.][]{mccracken_multinational_2001,kolling_problem_1999},
or a survey of practices
\autocite[e.g.][]{pears_survey_2007-1,robins_learning_2003} we used
the `cited by' list to find additional relevant papers.
